---
title: "LinearRegProject"
author: "Nan Zhang"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Should This Loan be Approved or Denied?

## Setup
```{r}
# Setup
SBA <- read.csv(file = "SBAnational.csv", header = T)
head(SBA,5)
```

## Section 1: Pre-Process

### Section 1.1: Data Cleaning
```{r}

```

### Section 1.2: Values Replacing
```{r}

```

### Section 1.3: Data Re-format/Transformation
```{r}

```

## Section 2: Explore the Variables

### Section 2.1: Y v.s X1 ...
```{r}

```

### Section 2.2: Y v.s X2 ...
```{r}

```

### Section 2.3: Y v.s X3 ...
```{r}

```

## Section 3: Fit Linear Model

### Section 3.1: ...
```{r}

```

### Section 3.2: ...
```{r}

```

### Section 3.3: ...
```{r}

```

### Section 3.4: Summary
```{r}

```

## Section 4: Residuals

### Section 4.1: ...
```{r}

```

### Section 4.2: ...
```{r}

```

### Section 4.3: ...
```{r}

```

## Section 5: Testing/Validation

### Section 5.1: ...
```{r}

```

### Section 5.2: ...
```{r}

```

### Section 5.3: ...
```{r}

```

## Section 6: Prediction

### Section 6.1: ...
```{r}

```

### Section 6.2: ...
```{r}

```

### Section 6.3: ...
```{r}

```

## Section 7: Conclusion
